\documentclass{article}\usepackage[left=2cm,right=2cm,top=3cm]{geometry}\usepackage[utf8]{inputenc}\setlength{\parindent}{0pt}\usepackage{tabularx}\begin{document}\begin{center}{\Large\hfill\hfill Weekly Team Task Report  \hfill 12, Wk 12}\end{center}\begin{center} \def\arraystretch{1.85} \begin{tabular}{|p{5em}|p{5em}|p{5em}|p{5em}|p{5em}|} \hline \multicolumn{4}{|c|}{\textbf{Team: }Astraea} & \multicolumn{1}{|c|}{\textbf{Date: } 4.10.20}\\ \hline\multicolumn{5}{|c|}{\textbf{Project Title: }Telescope Mirror Communication and Control System}\\\hline \textbf{Michael} & \textbf{Peter} & \textbf{Adam} & \textbf{Trey} & \textbf{Brandon} \\ Present & Present & Present & Present & Present \\ On-time & On-time & On-time & On-time & On-time \\\hline \end{tabular}\end{center}\textbf{Recent Meetings:}\\Client Meeting 4.10.20\\\\{\Large\textbf{TASKS COMPLETED since last meeing:}}\\\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Order Pi Parts \& Laptop & \textbf{Task Initiation: }3.27.20 & \textbf{Orig. Due Date: }3.30.20 & \textbf{Status: }100\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }Adam (100\%)}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Contact Henrique to order new Pi, laptop, sd card, and Pi case}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Parts are ordered}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Make changes to UGRADS abstract & \textbf{Task Initiation: }3.23.20 & \textbf{Orig. Due Date: }4.6.20 & \textbf{Status: }N/A\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }No one had any comments on this, so I (Adam) left it as it is...}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Abstract was not edited}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Capstone Presentation Dry Run: Intro & \textbf{Task Initiation: }3.29.20 & \textbf{Orig. Due Date: }4.10.20 & \textbf{Status: }50\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }Adam (100\%)}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Write script, make slides, and record Intro for Capstone Presentation Dry Run}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Video of good quality that does a good job of telling our story.}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Capstone Presentation Dry Run: Solution & \textbf{Task Initiation: }3.29.20 & \textbf{Orig. Due Date: }4.10.20 & \textbf{Status: }100\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }Mike}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Outline our solution and compare to existing setup}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Video section recorded.}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Capstone Presentation Dry Run: Problem Overview & \textbf{Task Initiation: }3.29.20 & \textbf{Orig. Due Date: }4.10.20 & \textbf{Status: }100\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }Peter}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Outline the current solution without bashing the previous hardware or mention satellite.}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Video section recorded.}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Capstone Presentation Dry Run: Schedule and Testing & \textbf{Task Initiation: }3.29.20 & \textbf{Orig. Due Date: }4.10.20 & \textbf{Status: }100\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }Mike}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Overview of schedule. Detailed list of planned tests.}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Video section recorded.}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Capstone Presentation Dry Run: Challenges and Resolutions & \textbf{Task Initiation: }3.29.20 & \textbf{Orig. Due Date: }4.10.20 & \textbf{Status: }100\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }Mike}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Tell the riveting story of our journey and all its trials and tribulations.}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Video section recorded.}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Capstone Presentation Dry Run: Future Work \& Conclusion & \textbf{Task Initiation: }3.29.20 & \textbf{Orig. Due Date: }4.10.20 & \textbf{Status: }50\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }Adam (100\%)}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Write script, edit powerpoint slides, record video of this section}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Video of decent quality.}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Capstone Presentation Dry Run: Compile all video together & \textbf{Task Initiation: }3.29.20 & \textbf{Orig. Due Date: }4.10.20 & \textbf{Status: }100\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }Adam (100\%)}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Complete video presentation by splicing all videos together, editing audio levels, screen resolutions, and put together final version of dry run}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Video of decent quality is put together.}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Software Testing Doc & \textbf{Task Initiation: }3.29.20 & \textbf{Orig. Due Date: }4.1.20 & \textbf{Status: }(99, 100)\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }All}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }The software document is completed.}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }A super great document about testing.}\\\hline\end{tabularx}\end{center}{\Large\textbf{This week’s Tasks: Work plan for coming week:}}\\\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Communicate with client our plan of action for the remainder of the term. & \textbf{Task Initiation: }4.2.20 & \textbf{Orig. Due Date: }4.10.20 & \textbf{Status: }10\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }Adam (100\%)}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Discuss plan of action with client so we are all on the same page.}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Discussed how to balance our efforts given the on-site restrictions and multiple upcoming deadlines (busy work intended for web app teams).}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Client: Submit preliminary poster for review & \textbf{Task Initiation: }4.10.20 & \textbf{Orig. Due Date: }4.15.20 & \textbf{Status: }0\%\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }ALL}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Client would like to look at the poster that we have worked on to give feedback}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Poster is sent to client}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Client: Submit Preliminary As-Is & \textbf{Task Initiation: }4.10.20 & \textbf{Orig. Due Date: }4.22.20 & \textbf{Status: }0\%\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }ALL}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Client needs As-Is report early to present to NRL in order to get funding for hiring us over the summer}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Preliminary As-Is is sent to client}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Client: Submit Moving Forward and Testing Plan & \textbf{Task Initiation: }4.10.20 & \textbf{Orig. Due Date: }4.22.20 & \textbf{Status: }0\%\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }ALL}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }To acquire funding from NRL -> Send client doc with testing plan + plan moving forward (things to implement, improvements to make, what we would do if we were to continue on this proect)}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Best case scenario -> Moving Forward doc is sent to Client. Funding is secured. We have jobs, yay!}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Utilize Thread Pool & \textbf{Task Initiation: }3.6.20 & \textbf{Orig. Due Date: }4.20.20 & \textbf{Status: }90\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }Brandon (100\%)}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }The thread pool code compiles, must create a workflow and main method for using thread pool on NeuronCon}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }A main.cpp file designed using the thread pool.}\\\hline\end{tabularx}\end{center}{\Large\textbf{Upcoming Tasks:}}\\\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Create and document useful aliases for BrainCon & \textbf{Task Initiation: }3.13.20 & \textbf{Orig. Due Date: }5.8.20 & \textbf{Status: }0\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }Mike (100\%)}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Create useful system admin aliases for BrainCon to facilitate easy system maintenance.}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Aliases created and documented.}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }User Manual & \textbf{Task Initiation: }3.23.20 & \textbf{Orig. Due Date: }4.24.20 & \textbf{Status: }0\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }Peter (50\%), Rest TBD}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Create the user manual for the system to give to JC so they can replicate/use the system}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }A manual for the system}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }BrainCon Code Documentation & \textbf{Task Initiation: }3.23.20 & \textbf{Orig. Due Date: }4.24.20 & \textbf{Status: }2\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }Trey (70\%) Peter (20\%) Adam (10\%)}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Document the code to limit future questions about source code and to allow future developers to read and understand our code.}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Well-documented code.}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }NeuronCon Code Documentation & \textbf{Task Initiation: }3.23.20 & \textbf{Orig. Due Date: }4.24.20 & \textbf{Status: }2\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }Adam (34\%) Mike (33\%) Brandon (33\%)}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Document the code to limit future questions about source code and to allow future developers to read and understand our code.}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Well-documented code.}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Circuit Diagrams & \textbf{Task Initiation: }3.27.20 & \textbf{Orig. Due Date: }4.24.20 & \textbf{Status: }1\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }Adam (70\%) Peter (30\%)}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Create circuit diagrams for all of the curcuits made for the project to allow future EE's to improve and understand the electronics.}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Circuit diagrams}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Finilaze Team Website & \textbf{Task Initiation: }4.8.20 & \textbf{Orig. Due Date: }5.8.20 & \textbf{Status: }90\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }Adam (100\%)}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Ensure website defeats that of all other teams both now and who have come before.}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Other teams defeated and in disbelief ("woah did it just resize?!?!?".}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Capstone Poster & \textbf{Task Initiation: }4.8.20 & \textbf{Orig. Due Date: }5.8.20 & \textbf{Status: }0\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }ALL}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Create poster for our project and submit with 20 min video.}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Poster created and video recorded; assignment submitted (emphasis on first three letters).}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Final Product Acceptance Demo & \textbf{Task Initiation: }4.8.20 & \textbf{Orig. Due Date: }5.8.20 & \textbf{Status: }0\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }ALL}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Final demonstration of solution. Discuss options with mentor due to site closure (do in summer).}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Team and mentor have come to a reasonable agreement and set time to demo in summer.}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Final Ass Built Report & \textbf{Task Initiation: }4.8.20 & \textbf{Orig. Due Date: }5.8.20 & \textbf{Status: }0\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }ALL}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Write yet another report filled with the abbreviation of bachelor of science.}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Team and mentor have come to a reasonable agreement and set due dates for the summer (donuts upon request).}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Final Delivery & \textbf{Task Initiation: }4.8.20 & \textbf{Orig. Due Date: }5.8.20 & \textbf{Status: }0\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }ALL}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Just when you thought there could be no more, another assignment surfaces and restores anger to the population.}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Team and mentor have come to a reasonable agreement and set due dates for the summer (VEGAN donuts upon request).}\\\hline\end{tabularx}\end{center}\end{document}