\documentclass{article}\usepackage[left=2cm,right=2cm,top=3cm]{geometry}\usepackage[utf8]{inputenc}\setlength{\parindent}{0pt}\usepackage{tabularx}\begin{document}\begin{center}{\Large\hfill\hfill Weekly Team Task Report  \hfill 11, Wk 11}\end{center}\begin{center} \def\arraystretch{1.85} \begin{tabular}{|p{5em}|p{5em}|p{5em}|p{5em}|p{5em}|} \hline \multicolumn{4}{|c|}{\textbf{Team: }Astraea} & \multicolumn{1}{|c|}{\textbf{Date: } 4.3.20}\\ \hline\multicolumn{5}{|c|}{\textbf{Project Title: }Telescope Mirror Communication and Control System}\\\hline \textbf{Michael} & \textbf{Peter} & \textbf{Adam} & \textbf{Trey} & \textbf{Brandon} \\ Present & Present & Present & Present & Present \\ On-time & On-time & On-time & On-time & On-time \\\hline \end{tabular}\end{center}\textbf{Recent Meetings:}\\Team Zoom Meeting 4.2.20\\\\{\Large\textbf{TASKS COMPLETED since last meeing:}}\\\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Discuss strategy and delegation for Capstone Dry Run (previously DR3) & \textbf{Task Initiation: }3.29.20 & \textbf{Orig. Due Date: }4.2.20 & \textbf{Status: }100\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }ALL}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Who will edit, what software, strategy, screen sharing, who does what part.}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Decided we will have Adam be the master editor with his critical gamer skills. Team is clear on what we would like to focus on and who is doing which part. Also created a living list of all diagrams needed for the presentation.}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Discuss strategy for remainder of the term & \textbf{Task Initiation: }3.29.20 & \textbf{Orig. Due Date: }4.4.20 & \textbf{Status: }100\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }ALL}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }See title}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Discussed how to balance our efforts given the on-site restrictions and multiple upcoming deadlines (busy work intended for web app teams).}\\\hline\end{tabularx}\end{center}{\Large\textbf{Removed to better focus efforts in response to limited site access:}}\\\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Convert code away from WiringPi & \textbf{Task Initiation: }3.13.20 & \textbf{Orig. Due Date: }4.10.20 & \textbf{Status: }11\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }Michael (100\%)}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }WiringPi seems to conflict with the PWM PiGPIO lib. PiGPIO also supports GPIO access and does not use the WiringPi virtual numbering (which has only confused things).}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Code converted to setup with and use PiGPIO commands. Pushed to repo.}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Test pins after conversion to PiGPIO & \textbf{Task Initiation: }3.13.20 & \textbf{Orig. Due Date: }4.10.20 & \textbf{Status: }0\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }TBD (dibs)}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Test that conversion to PiGPIO addresses the correct pins and outputs the correct signal.}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Code tested and confirmed to work.}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Research and implement sending command line instructions from within C code & \textbf{Task Initiation: }3.13.20 & \textbf{Orig. Due Date: }4.10.20 & \textbf{Status: }0\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }Mike (100\%)}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }It is useful (yet dangerous) to accept command line input from code. Research protocol in C and implement test code.}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Test code written and tested.}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Determine packet structure for including command line instructions. & \textbf{Task Initiation: }3.13.20 & \textbf{Orig. Due Date: }4.10.20 & \textbf{Status: }0\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }Trey (50\%) Mike (50\%)}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Decide on a way to include, differentiate, and act on command line instructions within packet.}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Design determined.}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Implement the architected design for command line instructions & \textbf{Task Initiation: }3.13.20 & \textbf{Orig. Due Date: }4.10.20 & \textbf{Status: }0\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }Trey (50\%) Mike (50\%)}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Trey will incorporate and differentiate the data. Mike will differentiate and execute the data.}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Data terminated.}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Put together demo doc & \textbf{Task Initiation: }3.27.20 & \textbf{Orig. Due Date: }4.3.20 & \textbf{Status: }0\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }All}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Put together demo summary for Gerard and JC documenting results and how to move forward}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Document is sent to JC and Gerard}\\\hline\end{tabularx}\end{center}{\Large\textbf{This week’s Tasks: Work plan for coming week:}}\\\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Order Pi Parts \& Laptop & \textbf{Task Initiation: }3.27.20 & \textbf{Orig. Due Date: }3.30.20 & \textbf{Status: }0\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }Adam (100\%)}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Contact Henrique to order new Pi, laptop, sd card, and Pi case}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Parts are ordered}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Order NAT parts & \textbf{Task Initiation: }3.27.20 & \textbf{Orig. Due Date: }3.30.20 & \textbf{Status: }0\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }Adam (100\%)}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Contact manufacturer of NATCon boxes and get new pair of DC-DC converters (ask for quote first and confirm with JC}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Parts are ordered}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Communicate with client our plan of action for the remainder of the term. & \textbf{Task Initiation: }4.2.20 & \textbf{Orig. Due Date: }4.6.20 & \textbf{Status: }10\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }Adam (100\%)}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Discuss plan of action with client so we are all on the same page.}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Discussed how to balance our efforts given the on-site restrictions and multiple upcoming deadlines (busy work intended for web app teams).}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Utilize Thread Pool & \textbf{Task Initiation: }3.6.20 & \textbf{Orig. Due Date: }3.29.20 & \textbf{Status: }70\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }Brandon (100\%)}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }The thread pool code compiles, must create a workflow and main method for using thread pool on NeuronCon}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }A main.cpp file designed using the thread pool.}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Capstone Presentation Dry Run & \textbf{Task Initiation: }3.29.20 & \textbf{Orig. Due Date: }4.10.20 & \textbf{Status: }10\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }ALL (parts delegated in team document; available upon request)}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Work on individual parts, requesting help as needed, and put together in final video.}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Video of good quality that does a good job of telling our story.}\\\hline\end{tabularx}\end{center}{\Large\textbf{Upcoming Tasks:}}\\\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }POSTPONED: Make changes to UGRADS abstract & \textbf{Task Initiation: }3.23.20 & \textbf{Orig. Due Date: }4.10.20 & \textbf{Status: }0\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }Adam (20\%), Trey (20\%), Peter (20\%), Mike(20\%), Peter (20\%)}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Develop a phenomenal abstract for UGRADS}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Abstract is submitted}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Create and document useful aliases for BrainCon & \textbf{Task Initiation: }3.13.20 & \textbf{Orig. Due Date: }4.10.20 & \textbf{Status: }0\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }Mike (100\%)}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Create useful system admin aliases for BrainCon to facilitate easy system maintenance.}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Aliases created and documented.}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }User Manual & \textbf{Task Initiation: }3.23.20 & \textbf{Orig. Due Date: }4.24.20 & \textbf{Status: }0\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }Peter (50\%), Rest TBD}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Create the user manual for the system to give to JC so they can replicate/use the system}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }A manual for the system}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }BrainCon Code Documentation & \textbf{Task Initiation: }3.23.20 & \textbf{Orig. Due Date: }4.24.20 & \textbf{Status: }2\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }Trey (70\%) Peter (20\%) Adam (10\%)}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Document the code to limit future questions about source code and to allow future developers to read and understand our code.}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Well-documented code.}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }NeuronCon Code Documentation & \textbf{Task Initiation: }3.23.20 & \textbf{Orig. Due Date: }4.24.20 & \textbf{Status: }2\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }Adam (34\%) Mike (33\%) Brandon (33\%)}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Document the code to limit future questions about source code and to allow future developers to read and understand our code.}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Well-documented code.}\\\hline\end{tabularx}\end{center}\begin{center}\def\arraystretch{1.85}\begin{tabularx}{\textwidth}{|X|X|X|X|}\hline\textbf{Task Title: }Circuit Diagrams & \textbf{Task Initiation: }3.27.20 & \textbf{Orig. Due Date: }4.24.20 & \textbf{Status: }1\% \\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Who (\%): }Adam (70\%) Peter (30\%)}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Description: }Create circuit diagrams for all of the curcuits made for the project to allow future EE's to improve and understand the electronics.}\\\hline\multicolumn{4}{|>{\hsize=\dimexpr4\hsize+4\tabcolsep+2\arrayrulewidth\relax}X|}{\textbf{Outcome: }Circuit diagrams}\\\hline\end{tabularx}\end{center}\end{document}